\documentclass[10pt]{article} 
\usepackage{csw} 
\usepackage{cswapa} 
\usepackage{times}
\usepackage{spverbatim}
\usepackage{multicol}

\begin{document} 
\cswtitleblock{
\cswtitle{Semantic Indexing}
\cswauthor{Anant Bhardwaj}{anantb@csail.mit.edu}
\cswaddress{}
}

\section{Introduction}
Majority of information retrieval and web search use the inverted index as the backbone for their keyword based search. Unfortunately, inverted index fail to capture the semantic of the language and thus keyword based approach can only go as far as giving the relevant hits. I propose semantic indexing scheme which can encode natural languages without losing semantic relationships.
 \\
 \\
The encoding of natural language would involve parsing of each sentence, deriving its semantic model and storing the encoded representation. Matthew Fay and Jodyann Coley in his work SemantcSQL have attempted to store natural language parses in SQL. While SemanticSQL does store parses of very simple sentences, it fails to encode and accurately recover the semantic information from the stored representation for complex sentences. The proposed indexing scheme should be able to derive semantic structure from complex sentences and store the derived semantic model, such that semantic information can be recovered accurately. 

\subsection{NLP Class Project (Ability to understand complex sentences)}
The NLP class project would involve adding the following capabilities to existing semantic SQL project. This would be done in collaboration with two more students taking the class.:
\begin{enumerate}
\item{
\textbf{Probabilistic Parsing}\\
Our system would incorporate a probabilistic sentence parser which would allow the system to intelligently identify the part-of-speech of previously unknown words and appropriately encode them.
}

\item{
\textbf{Multiple Adverbs and Prepositional Phrases}\\
The current implementation only allows a single occurrence of location, adverb, and instrument phrases. Our system would allow sentences such as \emph{John slept under the tree in the park} to be understood, and the question ``Where did John sleep?'' would return \emph{under the tree in the park'}.
}

\item{
\textbf{Noun Phrases with Relative Classes, and Time}
\emph{
\begin{enumerate}
\item{Show me all the states with population greater than 1 million.}
\item{Show me all the widgets that were selected yesterday.}
\end{enumerate}
}
}

\item{
\textbf{Either-Or and Neither-Nor}
\emph{
\begin{enumerate}
\item{Josh ate either bread or apple (exclusive)}
\item{Josh didn't eat either bread or apple (negation, inclusive)}
\item{Josh ate neither bread nor apple (inclusive).}
\end{enumerate}
}
}

\item{
\textbf{Intersective vs. Non-Intersective Adjectives}\\
\emph{\textbf{Intersective Adjectives:}}
\emph{
\begin{enumerate}
\item{The car is a red Volkswagen.}
\item{Grace is a hairy brown dog.}
\item{We drove up yet another serpentine mountain road.}
\end{enumerate}
}

\emph{\textbf{Non-Intersective Adjectives:}}
\emph{
\begin{enumerate}
\item{Viktor is a former Catholic.}
\item{The alleged thief has arrived in court.}
\end{enumerate}
}
}


\item{
\textbf{Complex Causality} \\
The current implementation only allows a primitive causality of 'if then' kind. Expanding it to more complex causality mapping would allow us handle complex causality.
\emph{
\begin{enumerate}
\item {Anna told Alex to return the chair because it was broken.}
\item {They moved here because of the work.}
\item{Because John is tired we decided to stay at home.}
\item{We can leave after the rain stops.}
\item{If Mary finishes her homework and the weather is good then Mary will go for a walk.}
\end{enumerate}
}

\emph{\textbf{Relating events based on time:}}
\emph{
\begin{enumerate}
\item{Did John come home after the fire alarm went off?}
\end{enumerate}
}
}


\item{
\textbf{Conjunctions and Disjunctions}
\emph{
\begin{enumerate}
\item{Depending on the weather, John will go for a walk or watch a movie.}
\end{enumerate}
}
}


\item{
\textbf{Quantifiers}\\
For instance, we would be able to answer questions like:
\emph{
\begin{enumerate}
\item{How many times have John watched the movie?}
\item{How much milk have John got in the fridge?}
\item{Is there any milk in the fridge?}
\end{enumerate}
}
}

\end{enumerate}

\section{Beyond NLP Class}
I plan to develop an infrastructure which has the capabilities to store and retrieve the encoded semantic model for the types of sentences described above and more. As of now, I am thinking of using SQL but the schema I have in mind is totally different from the schema used in SemanticSQL.

\section{Schema}
\begin{multicols}{2}

\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Events}
\\
\hline
id\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Actions}
\\
\hline
id\\
\hline
action\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Objects}
\\
\hline
id\\
\hline
object\\
\hline
\end{tabular}




\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Adjectives}
\\
\hline
id\\
\hline
adjective\\
\hline
\end{tabular}





\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Adverbs}
\\
\hline
id\\
\hline
adverb\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Tenses}
\\
\hline
id\\
\hline
tense\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Actions}
\\
\hline
id\\
\hline
event\_id\\
\hline
action\_id\\
\hline
tense\_id\\
\hline
\end{tabular}




\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Agents}
\\
\hline
id\\
\hline
event\_id\\
\hline
agent\_id(object\_id)\\
\hline
\end{tabular}
\label{table:nonlin}




\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Patients}
\\
\hline
id\\
\hline
event\_id\\
\hline
patient\_id(object\_id)\\
\hline
\end{tabular}




\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Instruments}
\\
\hline
id\\
\hline
event\_id\\
\hline
instrument\_id(object\_id)\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Beneficiaries}
\\
\hline
id\\
\hline
event\_id\\
\hline
beneficiary\_id(object\_id)\\
\hline
\end{tabular}


\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Locations}
\\
\hline
id\\
\hline
event\_id\\
\hline
location\_id(object\_id)\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Adjectives}
\\
\hline
id\\
\hline
event\_id\\
\hline
object\_id\\
\hline
adjective\_id\\
\hline
\end{tabular}



\begin{tabular}{|p{0.95\linewidth}|} 
\hline                   
\textbf{Event-Adverbs}
\\
\hline
id\\
\hline
event\_id\\
\hline
action\_id\\
\hline
adverb\_id\\
\hline
\end{tabular}

\end{multicols}











\bibliography{references} \bibliographystyle{cswapa}
\end{document} 
